\HeaderA{addtable2plot}{Add a table of values to a plot}{addtable2plot}
\keyword{misc}{addtable2plot}
\begin{Description}\relax
Displays a table of values at a user-specified position on an existing plot
\end{Description}
\begin{Usage}
\begin{verbatim}
 addtable2plot(x,y=NULL,table,lwd=par("lwd"),bty="n",bg=par("bg"),
  cex=1,xjust=0,yjust=1,box.col=par("fg"),text.col=par("fg"),
  display.colnames=TRUE,display.rownames=FALSE,hlines=FALSE,title=NULL)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{x,y}] Either x and y coordinates to locate the table or an
\samp{xy.coords} object.
\item[\code{table}] A data frame, matrix or similar object that will be displayed.
\item[\code{lwd}] The line width for the box and horizontal dividers.
\item[\code{bty}] Whether to draw a box around the table ("o") or not ("n").
\item[\code{bg}] The background color for the table.
\item[\code{cex}] Character expansion for the table.
\item[\code{xjust,yjust}] Positioning for the table relative to \samp{x,y}.
\item[\code{box.col}] The color for the box and lines.
\item[\code{text.col}] The color for the text.
\item[\code{display.colnames}] Whether to display the column names in the table.
\item[\code{display.rownames}] Whether to display the row names in the table.
\item[\code{hlines}] Whether to draw horizontal lines between each row of the table.
\item[\code{title}] Optional title placed over the table.
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
\samp{addtable2plot} displays the values in \samp{table} at a position in user
coordinates specified by \samp{x,y}. The two justification arguments,
\samp{xjust} and \samp{yjust} are the same as in the \samp{legend} function,
and \samp{addtable2plot} has been programmed to be as similar to \samp{legend}
as possible. The defaults are those that were most popular in scientific
journals at the time of programming.
\end{Details}
\begin{Value}
nil
\end{Value}
\begin{Author}\relax
Original by John Kane, mods by Jim Lemon and Brian Diggs
\end{Author}
\begin{SeeAlso}\relax
\samp{\LinkA{legend}{legend}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
 testdf<-data.frame(Before=c(10,7,5),During=c(8,6,2),After=c(5,3,4))
 rownames(testdf)<-c("Red","Green","Blue")
 barp(testdf,main="Test addtable2plot",ylab="Value",
  names.arg=colnames(testdf),col=2:4)
 # show most of the options
 addtable2plot(2,8,testdf,bty="o",display.rownames=TRUE,hlines=TRUE,
  title="The table")
\end{ExampleCode}
\end{Examples}

