\HeaderA{arctext}{Display text on a circular arc.}{arctext}
\keyword{misc}{arctext}
\begin{Description}\relax
\samp{arctext} displays a string along a circular arc, rotating each
letter. This may not work on all devices, as not all graphic devices
can rotate text to arbitrary angles. The output looks best on a 
Postscript or similar device that can rotate text without distortion.
Rotated text often looks very ragged on small bitmaps.

If the user passes a value for
\samp{start}, this will override any value passed to \samp{middle}.
If the plot area is not square, see \samp{par(pty="s")}, the arc will
be somewhat elliptical.
\end{Description}
\begin{Usage}
\begin{verbatim}
 arctext(x,center=c(0,0),radius=1,start=NA,middle=pi/2,stretch=1,cex=1,...)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] A character string.
\item[\code{center}] The center of the circular arc in x/y user units.
\item[\code{radius}] The radius of the arc in user units.
\item[\code{start}] The starting position of the string in radians.
\item[\code{middle}] The middle position of the string in radians.
\item[\code{stretch}] How much to stretch the string for appearance.
\item[\code{cex}] The character expansion factor.
\item[\code{...}] additional arguments passed to \samp{text}.
\end{ldescription}
\end{Arguments}
\begin{Value}
nil
\end{Value}
\begin{Author}\relax
Jim Lemon - Thanks to Suhas Parandekar for the idea.
\end{Author}
\begin{SeeAlso}\relax
\samp{\LinkA{text}{text}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
 plot(0,xlim=c(1,5),ylim=c(1,5),main="Test of arctext",xlab="",ylab="",
  type="n")
 arctext("bendy like spaghetti",center=c(3,3),col="blue")
 arctext("bendy like spaghetti",center=c(3,3),radius=1.5,start=pi,cex=2)
 arctext("bendy like spaghetti",center=c(3,3),radius=0.5,
  start=pi/2,stretch=1.2)
\end{ExampleCode}
\end{Examples}

