\HeaderA{boxed.labels}{Place labels in boxes}{boxed.labels}
\keyword{misc}{boxed.labels}
\begin{Description}\relax
Places labels in boxes on an existing plot
\end{Description}
\begin{Usage}
\begin{verbatim}
 boxed.labels(x,y=NA,labels,
  bg=ifelse(match(par("bg"),"transparent",0),"white",par("bg")),
  border=TRUE,xpad=1.2,ypad=1.2,srt=0,cex=1,adj=0.5,...)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{x,y}] x and y position of the centers of the labels. \samp{x} can be an
\samp{\LinkA{xy.coords}{xy.coords}} list.
\item[\code{bg}] The fill color of the rectangles on which the labels are displayed
(see Details).
\item[\code{labels}] Text strings
\item[\code{border}] Whether to draw borders around the rectangles.
\item[\code{xpad,ypad}] The proportion of the rectangles to the
extent of the text within.
\item[\code{srt}] Rotation of the labels. If 90 or 270 degrees, the box will be
rotated 90 degrees.
\item[\code{cex}] Character expansion. See \samp{text}.
\item[\code{adj}] left/right adjustment. If this is set outside the function,
the box will not be aligned properly.
\item[\code{...}] additional arguments passed to \samp{text}.
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
The label(s) are displayed on a rectangular background. This may be useful
for visibility and is the reason that "transparent" background is not available.
Only right angle rotations are allowed in \samp{boxed.labels}. \emph{Important
change}: \samp{xpad} and \samp{ypad} are now the full proportion of
the box to text, not half. The user can now call \samp{cylindrect} or
\samp{gradient.rect} for the background rectangle.
\end{Details}
\begin{Value}
nil
\end{Value}
\begin{Note}\relax
This function is best for regularly spaced labels where overlapping is
not a problem. See \samp{\LinkA{thigmophobe.labels}{thigmophobe.labels}} for placing labels 
where overlap is likely.
\end{Note}
\begin{Author}\relax
Jim Lemon
\end{Author}
\begin{SeeAlso}\relax
\samp{\LinkA{spread.labels}{spread.labels}}, \samp{\LinkA{thigmophobe.labels}{thigmophobe.labels}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
 x<-rnorm(10)
 y<-rnorm(10)
 plot(x,y,type="p")
 nums<-c("one","two","three","four","five","six","seven","eight","nine","ten")
 boxed.labels(x,y-0.1,nums)
 # now label a barplot
 xpos<-barplot(c(1,3,2,4))
 boxed.labels(xpos,0.5,nums[1:4])
 # perform a PCA on the "swiss" dataset and plot the first two components
 data(swiss)
 swiss.pca<-prcomp(swiss)
 plot(swiss.pca$rotation[,1:2],xlim=c(-1,0.2),main="PCA of swiss dataset",
  type="n")
 boxed.labels(swiss.pca$rotation[1:6],swiss.pca$rotation[7:12],ypad=1.5,
  colnames(swiss),bg=c("red","purple","blue","blue","darkgreen","red"),
  col="white")
\end{ExampleCode}
\end{Examples}

