\HeaderA{tab.title}{Display the title of a plot as a colored tab.}{tab.title}
\keyword{misc}{tab.title}
\begin{Description}\relax
Display the title of a plot as a colored tab.
\end{Description}
\begin{Usage}
\begin{verbatim}
 tab.title(label,text.col=par("fg"),tab.col=par("bg"),border=par("fg"),
  lwd=par("lwd"),cex=1.5,pad.mult=1.6,radius=0)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{label}] The title for the plot.
\item[\code{text.col}] The color for the title text.
\item[\code{tab.col}] The color for the tab fill.
\item[\code{border}] The color for the tab border.
\item[\code{lwd}] The line width for the border.
\item[\code{cex}] Character expansion for the title.
\item[\code{pad.mult}] How much higher to make the tab relative to the label.
\item[\code{radius}] What proportion of the tab corners to round off.
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
\samp{tab.title} displays the plot title in a colored tab. The tab can be
rounded at the upper corners by specifying the proportion of the tab
height to be rounded as a number between 0 and 1. If the tab is too high
to fit on the figure region, a warning will be displayed and the tab will
still be shown.
\end{Details}
\begin{Value}
nil
\end{Value}
\begin{Author}\relax
Jim Lemon
\end{Author}
\begin{SeeAlso}\relax
\samp{\LinkA{polygon}{polygon}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
 testx<-matrix(cumsum(rnorm(30)^2)+1,nrow=10)
 stackpoly(testx,main="",
  xaxlab=c("One","Two","Three","Four","Five",
  "Six","Seven","Eight","Nine","Ten"),staxx=TRUE)
 tab.title("Three Squiggly Lines",tab.col="yellow",radius=0.5)
\end{ExampleCode}
\end{Examples}

