\HeaderA{triax.frame}{Triangle plot frame}{triax.frame}
\keyword{misc}{triax.frame}
\begin{Description}\relax
Display a three axis frame with optional grid.
\end{Description}
\begin{Usage}
\begin{verbatim}
 triax.frame(main="",at=seq(0.1,0.9,by=0.1),
 axis.labels=NULL,tick.labels=NULL,col.axis="black",cex.axis=1,cex.ticks=1,
 align.labels=TRUE,show.grid=FALSE,col.grid="gray",lty.grid=par("lty"),
 cc.axes=FALSE)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{main}] The title of the triangle plot. Defaults to nothing.
\item[\code{at}] The tick positions on the three axes.
\item[\code{axis.labels}] Labels for the three axes in the order bottom, right
left. Defaults to the column names.
\item[\code{tick.labels}] The tick labels for the axes.
Defaults to argument \samp{at} (proportions).
\item[\code{col.axis}] Color of the triangular axes, ticks and labels.
\item[\code{cex.axis}] Character expansion for axis labels.
\item[\code{cex.ticks}] Character expansion for the tick labels.
\item[\code{align.labels}] Logical - whether to align axis and tick labels with
the axes.
\item[\code{show.grid}] Whether to display grid lines at the ticks.
\item[\code{col.grid}] Color of the grid lines. Defaults to gray.
\item[\code{lty.grid}] Type of line for the grid.
\item[\code{cc.axes}] Whether to align the axes clockwise or counterclockwise.
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
\samp{triax.frame} displays a triangular plot area on which proportions
or percentages may be displayed. An optional grid may also be displayed.
If \samp{cc.axes} is TRUE, both the axes and axis ticks will be in
reverse order.
\end{Details}
\begin{Value}
nil
\end{Value}
\begin{Author}\relax
Jim Lemon
\end{Author}
\begin{SeeAlso}\relax
\samp{\LinkA{triax.points}{triax.points}},\samp{\LinkA{triax.abline}{triax.abline}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
 triax.frame(main="DEFAULT")
 triax.frame(main="Clockwise axes",cc.axes=TRUE)
\end{ExampleCode}
\end{Examples}

