\HeaderA{oz.windrose}{Display an Australian wind rose.}{oz.windrose}
\keyword{misc}{oz.windrose}
\begin{Description}\relax
Displays a wind rose in the style used by the Australian
Bureau of Meteorology.
\end{Description}
\begin{Usage}
\begin{verbatim}
 oz.windrose(windagg,speed.col=c("#dab286","#fe9a66","#ce6733","#986434"),
  speed.width=c(0.2,0.4,0.6,0.8),show.legend=TRUE,legend.pos=27,...)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{windagg}] A matrix of percentages with the rows representing
speed ranges and the columns indicating wind directions.
\item[\code{speed.col}] Colors representing speed ranges.
\item[\code{speed.width}] Half widths of the bars representing speed ranges.
\item[\code{show.legend}] Logical indicating whether to display a legend.
\item[\code{legend.pos}] The vertical position of the wind rose legend. The
Australian Bureau of Meteorology displays the legend at the top of
the plot
\item[\code{...}] additional arguments passed to \samp{plot}.
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
\samp{oz.windrose} displays a wind rose in the style used by the Australian
Bureau of Meteorology. Each limb represents a bin of wind directions, and 
there are conventionally eight bins. If \samp{windagg} has more than eight
columns, more limbs will be displayed. The rows of \samp{windagg} represent
the speed ranges used by the Australian Bureau of Meteorology (0, 0-10, 
10-20, 20-30 and over 30 in km/hour). The diameter of the central circle is
calculated as (percent calm observations)/(number of direction bins). The
remaining grid circles are spaced from the circumference of the "Calm"
circle.
\end{Details}
\begin{Value}
nil
\end{Value}
\begin{Note}\relax
If a title is desired, remember to move the legend to the bottom 
of the plot. If the function is passed values that do not sum to 100, the
resulting plot will at best be misleading.
\end{Note}
\begin{Author}\relax
Jim Lemon (thanks to Anna in the Sydney BoM office)
\end{Author}
\begin{SeeAlso}\relax
\samp{\LinkA{oz.windrose.legend}{oz.windrose.legend}}, \samp{\LinkA{draw.circle}{draw.circle}}, 
\samp{\LinkA{bin.wind.records}{bin.wind.records}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
 windagg<-matrix(c(8,0,0,0,0,0,0,0,4,6,2,1,6,3,0,4,2,8,5,3,5,2,1,1,
  5,5,2,4,1,4,1,2,1,2,4,0,3,1,3,1),nrow=5,byrow=TRUE)
 oz.windrose(windagg)
\end{ExampleCode}
\end{Examples}

