\HeaderA{fullaxis}{Add an axis with a line to the edge of the plot}{fullaxis}
\keyword{misc}{fullaxis}
\begin{Description}\relax
As \samp{axis}, but draws a "box" line in the same color as the axis.
\end{Description}
\begin{Usage}
\begin{verbatim}
 fullaxis(side=1,at=NULL,labels=TRUE,line=NA,pos=NA,outer=FALSE,
 font=NA,lty="solid",lwd=1,lwd.ticks=lwd,col=NULL,col.ticks=NULL,
 hadj=NA,padj=NA,...)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{side}] The side of the plot to draw the axis
\item[\code{at}] Optional positions in user units for the tick marks.
\item[\code{labels}] Optional labels for the tick marks.
\item[\code{line}] Optional line into the margin.
\item[\code{pos}] Optional position in user units for the axis. Defaults to the edge.
\item[\code{outer}] Whether to use the outer margin as for \samp{axis}.
\item[\code{font}] Font for the labels.
\item[\code{lty}] Line type.
\item[\code{lwd}] Line width for the axis.
\item[\code{lwd.ticks}] Line width for the ticks.
\item[\code{col}] color for the axis and tick marks. See Details for label color.
\item[\code{col.ticks}] Color for the tick marks if different from the axis.
\item[\code{hadj,padj}] Justification for the labels. See \samp{axis}.
\item[\code{...}] Further arguments passed to \samp{axis}.
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
\samp{fullaxis} draws a line to the edges of the plot and then calls
\samp{axis} to draw an axis. \samp{fullaxis} is mainly useful for drawing a
colored axis on a boxed plot. In order to get the tick labels the same color as
the axis and ticks, pass the \samp{col.axis} argument as well as \samp{col}.
See the example for some useful tips.
\end{Details}
\begin{Value}
The positions of the tick marks in user units.
\end{Value}
\begin{Author}\relax
Jim Lemon
\end{Author}
\begin{SeeAlso}\relax
\samp{\LinkA{axis}{axis}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
 plot(runif(20,-1,1),runif(20,-1,1),xlim=c(-1,1.5),main="Demo of fullaxis",
  xlab="X",ylab="Y",axes=FALSE)
 fullaxis(1,col="red")
 fullaxis(2,col="blue",col.axis="blue")
 fullaxis(4,at=c(-0.5,0,0.5),labels=c("Negative","Zero","Positive"),pos=1.2,
  col="green",las=1)
 # add a top line to complete the "box"
 xylim<-par("usr")
 segments(xylim[1],xylim[4],xylim[2],xylim[4])
\end{ExampleCode}
\end{Examples}

